### 2025-01-26 our_article/MCM_article/article_file.tex
论文重要更新

        \subsection{Notations}
      % table
      \begin{table}[H]
        \centering
        \caption{Notations}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $\mathbf{X}$ & Vector $[N_{wd},N_{crp},N_{pst},N_{ins},...,C_{hc},C_{pc}]^T$ to describe the system,etc. \\
          $wd$ & Subscription for weeds \\
          $crp$ & Subscription for crops \\
          $pst$ & Subscription for pest(who consumes crops) \\
          $ins$ & Subscription for other insects(who consume weeds) \\
          $bd$ & Subscription for small birds(herbivorous) \\
          $Bd$ & Subscription for huge birds(carnivorous) \\
          $bt$ & Subscription for bats \\
          $snk$ & Subscription for snake \\
          $frg$ & Subscription for frog \\
          $HC$ & Subscription for herbicide \\
          $PC$ & Subscription for pesticide \\
          $C_i$ & Concentration of certain chemical \\
          $N_i$ & Numbers of certain species \\
          $W_i$ & Biomass of certain species \\
          $w_i$ & Average mass of individuals of certain individuals \\
          $r_i$ & Natural growth gate of certain population\\
          $\mathscr{K}_i$ & Carrying capacity of certain population\\
          $\alpha$ & The effect of chemical concentration on growth rate\\
          $\beta_{i \rightarrow j}$ & Interspecific competition factor\\
          $\gamma$ & Activity of decomposer\\
          $A_i,B_i$ & Effect of the predator-prey relationship on population $i$ (specified coefficient).\\
          $N,P,K$ & Chemical elements\\
          \bottomrule
        \end{tabular}
        \label{tab:Notations}
      \end{table}

@@

      \subsection{Model II: }
      \begin{figure}[H]
          \centering
          \includegraphics[width=0.5\linewidth]{images/food_web.pdf}
          \caption{Food web for NGLG Model}
          \label{fig:NGLG_FoodWeb}
      \end{figure}
      \subsection{Model III: }
      \subsection{Model IV: }
  \section{Application of the Models}

>>>>

        \subsection{Notations}
      % table
      \begin{table}[H]
        \centering
        \caption{Notations}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $\mathbf{X}$ & Vector $[N_{wd},N_{crp},N_{pst},N_{ins},...,C_{hc},C_{pc}]^T$ to describe the system,etc. \\
          $wd$ & Subscription for weeds \\
          $crp$ & Subscription for crops \\
          $pst$ & Subscription for pest(who consumes crops) \\
          $ins$ & Subscription for other insects(who consume weeds) \\
          $bd$ & Subscription for small birds(herbivorous) \\
          $Bd$ & Subscription for huge birds(carnivorous) \\
          $bt$ & Subscription for bats \\
          $snk$ & Subscription for snake \\
          $frg$ & Subscription for frog \\
          $HC$ & Subscription for herbicide \\
          $PC$ & Subscription for pesticide \\
          $C_i$ & Concentration of certain chemical \\
          $N_i$ & Numbers of certain species \\
          $W_i$ & Density of biomass of certain species \\
          $w_i$ & Average mass density of individuals of certain individuals \\
          $r_i$ & Natural growth gate of certain population\\
          $\mathscr{K}_i$ & Carrying capacity of certain population\\
          $\alpha$ & The effect of chemical concentration on growth rate\\
          $\beta_{i \rightarrow j}$ & Interspecific competition factor\\
          $\gamma$ & Activity of decomposer\\
          $A_i,B_i$ & Effect of the predator-prey relationship on population $i$ (specified coefficient).\\
          $D_i,E_i$ & Effect of shortage of food on population $i$ (specified coefficient)\\
          $N,P,K$ & Chemical elements\\
          \bottomrule
        \end{tabular}
        \label{tab:Notations}
      \end{table}

@@

      \subsection{Model II: }
        Model I is quite simple and aims to construct a basic short-term model. 
        Considering the impact of long-term environmental factors, 
        in order to better simulate the long-term evolutionary behavior of the ecosystem model, 
        we will progressively introduce the effects of simplified agricultural cycles, 
        seasonality, soil fertility, and random factors on the system dynamics model. 
        Furthermore, we will consider the impact of chemical use, 
        specifically the application of herbicides and pesticides, on the system, 
        building upon this natural agricultural ecosystem model.

        \subsubsection{Agricultural Cycle}
          According to rice production in Indonesia \cite{cite}, 
          rice production in Southeast Asia follows a three-crop-per-year pattern. 
          We assume that February, June, and October are the overlapping periods of two agricultural cycles 
          (from the last post-harvest period to the new planting period). 
          During the overlapping period, the rice population re-enters the food web in the form of seeds after harvesting, 
          starting a new agricultural cycle. The mature rice straw, as an agricultural byproduct, 
          remains in the ecosystem after harvesting, and after being treated by methods such as burning or returning to the field, 
          the rice biomass is decomposed and ingested by decomposers and insects, ultimately decreasing to zero.

          Based on the literature review \cite{cite}, 
          the biomass fate of mature rice during each overlapping period can be uniformly described by the figure below \cite{cite}. 
          Since decomposers' biomass is not considered in our food web model, 
          we only analyze the impact of decomposed rice straw residue (1) on the producers—namely rice and weeds—in the new cycle. 
          For further details, refer to the soil fertility section later in the paper.

          For simplification of the model, 
          the biomass change of the rice population during each overlapping period is represented 
          by a biomass step function at specific time points in the mathematical model (i.e., the system of difference equations). 
          Since $t=0$ corresponds to the start of the first planting season, with one year assumed to have 52 weeks, 
          and each week being a time step, based on the rice production pattern \cite{cite}, 
          we define the step moments at week 0, week 17, and week 34 of each year. The biomass of rice at these times follows:

          \begin{equation}
          W_{crp}|_{t=n}=0.1W_{crp}|_{t=n-1}, \quad n = 52k, 52k+17, 52k+34, \quad (year\, k \geqslant 0, \, week\, n \geqslant 1)
          \end{equation}

          When considering the impact of rice straw on insect biomass, 
          we treat rice straw as the 'prey' of insects and use the modified Lotka-Volterra (LG) predator-prey model to characterize this effect. 
          At each step moment, rice straw enters the food web model with an initial biomass of $0.09W_{crp}$, and $r_{stw} = 0$. 
          Thus, the rice straw-insect model is established as:

          \begin{equation}
          \frac{\mathrm{d}W_{stw}}{\mathrm{d}t} = \frac{A_{stw} W_{stw} W_{ins}}{1 + B_{stw} W_{stw}} \quad (t \neq n)
          \end{equation}

          \begin{equation}
          W_{stw}|_{t=n} = W_{stw}|_{t=n-1} + 0.09 W_{crp}|_{t=n-1},\\
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1)
          \end{equation}

          The difference equation for insect biomass is modified as follows:

          \begin{equation}
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t} = r_{ins} W_{ins} \left[ 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} + W_{stw} \right)} \right] - \frac{A_{ins} W_{ins} W_{bd}}{1 + B_{ins} W_{ins}}
          \end{equation}

        \subsubsection{Seasonality}
          The seasonal influences primarily include factors such as light, 
          climate (temperature, precipitation), and biological habits, 
          all of which have significant direct effects on both $r$ and $\mathscr{K}$ within populations. 
          Considering that many of these factors are difficult to quantify precisely, 
          we refer to \cite{cite} and set sinusoidal perturbations in the periodic parameter $p(T)$ as follows:

          \begin{equation}
          p(t) = \bar{p} \left[ 1 + \epsilon \sin (\Omega t + \phi) \right]
          \end{equation}

          Specifically, in the LV-LG model mentioned above, 
          for population $i$, the values of $r_i$ and $K_i$ are defined as follows:

          \begin{align}
            r_i &= \bar{r}_i \left[ 1 + \epsilon_i \sin \left( \Omega_i t + \phi_i \right) \right] \\
            \mathscr{K}_i &= \bar{\mathscr{K}}_i \left[ 1 + \epsilon_i \sin \left( \Omega_i t + \phi_i' \right) \right], \quad \left( i = \text{crp or wd} \right) \\
            D_i &= \frac{\bar{D}_i'}{1 + \epsilon_i \sin \left( \Omega_i t + \phi_i' \right)}, \quad \left( i \neq \text{crp or wd} \right)
          \end{align}

          Where $\bar{r}_i$ and $\bar{\mathscr{K}}_i$ are the corresponding periodic means, 
          which can be treated as constants; $\Omega_i$ is the seasonal fluctuation angular frequency, 
          and $T = \frac{2\pi}{\Omega}$ is the seasonal fluctuation period; 
          $\epsilon_i$ is the seasonal impact parameter. Since $r_i, \mathscr{K}_i \geqslant 0$, 
          it follows that $-1 \leqslant \epsilon_i \leqslant 1$; $\phi_i$ and $\phi_i'$ are the phases, 
          with $0 \leqslant \phi_i < 2\pi$, which characterize the asynchronous fluctuations of biomass in different species.

          It can be mathematically proven that, after incorporating these variations, 
          the LV-LG model system theoretically possesses non-trivial stable points when the parameters are within a certain range. 
          When the system is near these points, the ecosystem can recover from small perturbations, 
          reaching a dynamic ecological equilibrium.

        \subsubsection{Soil Fertility}
        \subsubsection{Random Factor}
        \subsubsection{Chemical Use}
      \subsection{Model III: }
        \begin{figure}[H]
          \centering
          \includegraphics[width=0.5\linewidth]{images/food_web.pdf}
          \caption{Food web for NGLG Model}
          \label{fig:NGLG_FoodWeb}
        \end{figure}
      \subsection{Model IV: }
  \section{Application of the Models}
